---
title: "p8105_hw6_rt2640"
author: "Riddhi Thakkar"
date: "11/30/2021"
output: github_document
---

```{r setup}
library(tidyverse)
library(modelr)
library(mgcv)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
set.seed(1)

```


### Question 1

```{r}
birthweight = read_csv("./data/birthweight.csv")
```

```{r}
bw_mod = birthweight %>% 
  mutate(
    babysex = case_when(
      babysex == 1 ~"male",
      babysex == 2 ~"female"),
    frace = case_when(
      frace == 1 ~"white",
      frace == 2 ~"black",
      frace == 3 ~"asian",
      frace == 4 ~"puerto_rican",
      frace == 8 ~"other",
      frace == 9 ~"unknown"),
    mrace = case_when(
      mrace == 1 ~"white",
      mrace == 2 ~"black",
      mrace == 3 ~"asian",
      mrace == 4 ~"puerto_rican",
      mrace == 8 ~"other"),
    malform = case_when(
      malform == 0 ~"absent",
      malform == 1 ~"present")
    )
```

```{r}
bw_guess1 = lm(bwt ~ ., data = bw_mod) %>% 
  broom::tidy()
bw_guess2 = lm(
  bwt ~ babysex + bhead + blength + delwt +gaweeks + parity + smoken, 
  data = bw_mod)
```

```{r}
guess = bw_mod %>% 
  modelr::add_residuals(bw_guess2) %>%  
  modelr::add_predictions(bw_guess2)
guess %>% 
ggplot(aes(x = resid,y=pred))+
  geom_point()
```

We first fitted a linear model using all the possible predictors and then did a shortened version of backward elimination just to get a prelim model to work with.

```{r}
model_1 = lm(bwt ~ blength + gaweeks, data = bw_mod)
model_2 = lm(bwt ~ bhead*blength*babysex, data = bw_mod)
```

```{r}
cv_df =
  crossv_mc(bw_mod, 100) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
#Next I’ll use mutate + map & map2 to fit models to training data and obtain corresponding RMSEs for the testing data.
cv_df = 
  cv_df %>% 
  mutate(
    guess_mod  = 
      map(train, ~lm(bwt ~ babysex + bhead + blength + delwt +gaweeks + parity + smoken, 
                     data = .x)),
    model_1  = 
      map(train, ~lm(bwt ~ blength + gaweeks, 
                     data = .x)),
    model_2  = 
      map(train, ~lm(bwt ~ bhead*blength*babysex, 
                     data = as_tibble(.x)))) %>% 
  mutate(rmse_guess = map2_dbl(guess_mod, test, ~rmse(model = .x, data = .y)),
         rmse_model_1    = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
         rmse_model_2 = map2_dbl(model_2, test, ~rmse(model = .x, data = .y)))
rmse_data = cv_df %>% 
  select(starts_with("rmse")) %>% 
pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model))
rmse_data %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

Model 1 is a model using length at birth and gestational age as main effects predictors and model 2 is a model using head circumference, length, sex and all their internal interactions. Guess is the model using a very truncated verison of backward elimination.



